Browsing the Web of Factual Claims

### 2008-09-18 papers/web_of_ideas/web_of_ideas.tex
More paper fleshing. Lots of nice figures and diagrams

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Browsing the Web of Factual Claims},
pdfauthor={Beth Trushkowski and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

@@

Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained within those documents. A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read. A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.

@@

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/redhighlight.png}
	\caption{Think Link highlights the key claims made by a page. Red means the claim is contentious.}
	\label{highlight}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/sidebar3.png}
	\caption{The margin shows a summary of the key claims made by the page}
	\label{margin}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/claim_popup.png}
	\caption{Click on a claim to see supporting or opposing evidence on other web pages}
	\label{claimview}
\end{figure}

@@

@@

@@

\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming exists''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and are not understood logically by Think Link.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a particular web site that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can have one or more topics that it is about, and a topic can have one or more more general topics. Topics are used both to organize, and to disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
\end{itemize}

@@

\subsection{Identifying factual claims on a page}

@@

\begin{figure}[t]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
	\caption{The claim selection window allows one to identify the claim a snippet is making}
	\label{snipsavefull}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
	\caption{Close up view of the claim selection window}
	\label{snipsavecrop}
\end{figure}

@@

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
	\caption{The Claim Browser}
	\label{fig:claimbrowser}
\end{figure}

@@

@@

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/oldpoint_search.png}
	\caption{Initial Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Browsing the Web of Factual Claims},
pdfauthor={Beth Trushkowski and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

@@

Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained on those pages. A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read. A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/highlight_crop.png}
	\caption{Key factual claims are highlighted}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claim_popup_crop2.png}
	\caption{Click on a claim to investigate evidence for and against}
	\label{claimview}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/sidebar_crop.png}
	\caption{The margin summarizes the key claims on the page}
	\label{margin}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/bookmark_icons.png}
	\caption{Icons used for Claims, Snippets, and Topics}
	\label{bookmark_icons}
	\end{center}
\end{figure}

%\begin{wrapfigure}{r}{4cm}
%	\begin{center}
%	\includegraphics[width=4cm]{../screenshots/bookmark_icons.png}
%	\end{center}
%\end{wrapfigure}
\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming exists''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and are not understood logically by Think Link.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a particular web site that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can have one or more topics that it is about, and a topic can have one or more more general topics. Topics are used both to organize, and to disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
\end{itemize}

@@

\subsection{Exploring factual claims on a page}

@@

@@

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/claimbrowse.png}
	\caption{The Claim Organizer contains two claim browsers}
	\label{fig:claimbrowser}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The Claim Browser Allows one to browse the argument graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/fullbrowser.png}
	\caption{The Enhanced claim browser adds additional controls}
	\label{enhancedbrowser}
	\end{center}
\end{figure}

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
	\caption{Process for creating a new snippet}
	\label{snipsavecrop}
	\end{center}
\end{figure*}

%\begin{figure}[tb]
%	\includegraphics[width=8.5cm]{../screenshots/snipsave_full.png}
%	\caption{The claim selection window allows one to identify the claim a snippet is making}
%	\label{snipsavefull}
%\end{figure}

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_crop.png}
	\caption{Close up view of the claim selection window}
	\label{snipsavecrop}
\end{figure}

@@

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
	\caption{Initial Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}
